lab_notebook

### 2018-11-09 lab_notebook.Rmd
edf turf data

number_species <- unique(stock$scientificname)
#341 different species

@@

@@

#RAM data wrangling
```{r}
ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

colnames(ram) <- c("stockid", "CommName", "Year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

@@

ITQ_projection_year <- ITQ_projection %>%
  unite(Name_Year, "CommName", "Year", sep = "-")
```

#Attemps at merging ITQ_projection with rams
Playing with Data

```{r}

IdOrig <- unique(ITQ_projection$IdOrig)
IdOrig
#337 species total

IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
IdOrig_implemented
#115 species with ITQ implemented

@@

##this doesn't work
RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)

>>>>

#number_species <- unique(stock$scientificname)
#341 different species

#cooperative data from "Conservation incentives and collective choices in cooperative fisheries" paper (Ovando et al 2013)
jc_coop <- read_csv("data/clean_cooperatives_data.csv")

@@

Playing with Data

@@

#RAM data wrangling
```{r}
ram <- select(timeseries_values_views, "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy")

@@

ITQ_projection_year <- ITQ_projection %>%
  unite(Name_Year, "CommName", "Year", sep = "-")

@@

##this doesn't work; gives you vector not updated data frame
RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)

#what happens when i just merge the two?
#test_merge <- merge(ITQ_projection_year, ram_merge, by = c("Name_Year"))
